\chapter{SUPPORTING LITERATURE}

\section{Overview}
Building a modern web application like the Alumni Management System requires standing on the shoulders of robust, open-source literature and documentation. In the development of this platform, several key framing documents, architecture guides, and styling frameworks were deeply analyzed.

\section{Laravel Documentation}
The primary literature driving the backend systems of the project is the official Laravel 12.x Documentation. This comprehensive guide dictates the structural MVC routing, Eloquent ORM relationships, and Blade templating methodologies used to render dynamic views such as the Profile Dashboard and the Posts Feed. By adhering to the documentation, secure authentication (via Laravel Breeze) and role-based middleware were efficiently integrated.

\section{Tailwind CSS Specifications}
To achieve a highly responsive and modern user interface, the Tailwind CSS component and utility class references were utilized. The literature provided by Tailwind Labs establishes rapid prototyping techniques, mobile-first design patterns, and responsive breakpoints, ensuring that the Alumni network is fully accessible on both desktop and mobile devices.

\section{Database ORM Theory}
General literature surrounding Object-Relational Mapping (ORM) and relational database design governed the creation of the schemas within PostgreSQL. Understanding the principles behind normalized tables, foreign-key constraints, and pivot tables (e.g., for the \texttt{likes} pivot connecting Users and Posts) was crucial to developing an efficient data architecture capable of scaling as the alumni network grows.
